\documentclass[11pt,letterpaper,roman]{moderncv}
\moderncvstyle[nosymbols,details,left]{casual}
\definecolor{myCustomColor}{RGB}{128, 0, 0}
\colorlet{color1}{myCustomColor}

\usepackage[lmargin=0.5in, rmargin=0.7in, tmargin=0.5in,bmargin=1in]{geometry}
\usepackage{kpfonts}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=color1,
    }

% remove symbols
\renewcommand*{\addresssymbol}{}
\renewcommand*{\mobilephonesymbol}{}
\renewcommand*{\fixedphonesymbol}{}
\renewcommand*{\faxphonesymbol}{}
\renewcommand*{\emailsymbol}{}
\renewcommand*{\homepagesymbol}{}
\renewcommand*{\linkedinsocialsymbol}{}
\renewcommand*{\twittersocialsymbol}{}
\renewcommand*{\githubsocialsymbol}{}

% length for column
\setlength{\hintscolumnwidth}{3cm}

% edit heading
\makeatletter
\RenewDocumentCommand{\section}{sm}{%
  \par\addvspace{5ex}%
  \phantomsection{}% reset the anchor for hyperrefs
  \addcontentsline{toc}{section}{#2}%
  \cvitem[0ex]{\strut\raggedleft\raisebox{\baseletterheight}{\color{white}\rule{\hintscolumnwidth}{0.4ex}}}{\strut\sectionstyle{#2}}%
  \par\nobreak\addvspace{2ex}\@afterheading}% to avoid a pagebreak after the heading
\makeatother

% edit footer
\nopagenumbers{}

% edit cventry 
\renewcommand*{\cventry}[7][.25em]{%
  \cvitem[#1]{#2}{%
    {\bfseries#3}%
    \ifthenelse{\equal{#4}{}}{}{ -- {\slshape#4}}%
    \ifthenelse{\equal{#5}{}}{}{\newline#5}%
    \ifthenelse{\equal{#6}{}}{}{\newline#6}%
    \strut%
    \ifx&#7&%
    \else{\newline{}\begin{minipage}[t]{\linewidth}\small#7\end{minipage}}\fi}}

% adjust color
\colorlet{color2}{black}
\colorlet{lastnamecolor}{color2}
\colorlet{firstnamecolor}{color2}
\colorlet{addresscolor}{black}
\colorlet{titlecolor}{black}
\colorlet{thepagecolor}{black}
\colorlet{headrulecolor}{white}

% adjust column width
\setlength{\separatorcolumnwidth}{0.05\textwidth}
\renewcommand{\listitemsymbol}{}

% adjust header formatting
\renewcommand*{\namefont}{\fontsize{24}{26}\bfseries}
\renewcommand*{\titlefont}{\fontsize{20}{22}\mdseries}
\renewcommand*{\addressfont}{\large\mdseries}

% adjust section formatting
\renewcommand*{\sectionfont}{\fontsize{14}{16}\bfseries\upshape}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\textcolor{color1}{#1}}}

% biographical info
\firstname{Gabriel}
\lastname{Correa}
\title{Curriculum Vitae}
\email{gbcorrea [at] umass [dot] edu}
\homepage{https://www.gabriel-correa.com}
%\phone{}
%\address{}

\begin{document}
%\setmainfont{Times New Roman}

\makeatletter
\renewcommand*{\makecvhead}{
    \hspace{\separatorcolumnwidth + \hintscolumnwidth}\parbox{20em}{
    \namestyle{{\@firstname} {\@lastname}} \vspace{1em} \\
    \addressstyle{\@email} \\
    \addressstyle{\@homepage}
    }\vspace{1em}
}
\renewcommand*{\makecvfoot}{
    \fancyfoot[c]{
        \thepage
    }
}
\makeatother

\makecvtitle

\section{Research Interests}

\cvitem{Broad:}{Syntax, morphology, syntax-semantics interface}
\cvitem{Narrow:}{Agreement \& case, person hierarchies, ergativity, applicative constructions, argument structure, information structure, clitic doubling, null subjects}

\cvitem{Languages I've worked on:}{Blackfoot (Algonquian); Latvian (Baltic); Brazilian Portuguese, Spanish (Romance)}

% previous info:
% \cvitem{Narrow:}{Agreement, case, information structure, clitic doubling, null subjects}

\section{Education}

\cventry{2025 -- Present}
    {University of Massachusetts, Amherst}
    {Amherst, MA}
    {PhD in Linguistics, in progress}
    {}
    {}

\cventry{2021 -- 2025}
    {The University of Chicago}
    {Chicago, IL}
    {B.A. in Linguistics with Honors, \emph{cum laude}}
    {Honors Thesis: \emph{Obviation as dependent case: Evidence from Blackfoot pronominal enclitics}\newline Advisor: \emph{Karlos Arregi}}
    {Cumulative GPA: 3.91 (Major GPA: 4.00)}

\section{Non-Degree Education}

\cventry{Sep -- Dec\\ 2024}
    {Universität Wien}
    {Vienna, Austria}
    {Study Abroad Program (via The University of Chicago)}
    {Courses in Advanced German and Civilization Studies}
    {}

\cventry{2022, 2024}
    {The NYI Global Institute of Cultural, Cognitive, and Linguistic Studies}
    {Remote}
    {Summer courses in Linguistics}
    {}
    {}

\cventry{2020, 2021}
    {University of São Paulo}
    {Remote}
    {Summer courses in Linguistics}
    {}
    {}

\section{Awards and Honors}
\cvitem{2025}{Leonard Bloomfield Prize (Department of Linguistics, The University of Chicago)}
\cvitem{2022, 2024, 2025}{Dean's List (The University of Chicago)}
\cvitem{2023 -- 2024}{Quad Undergraduate Scholar (The University of Chicago)}
\cvitem{2023}{College Summer Institute Scholar (The University of Chicago)}
\cvitem{2023}{Sapir Scholar (Department of Linguistics, The University of Chicago)}
\cvitem{2020}{Latin American Phoenix Scholar (The University of Chicago)}

\newpage
\section{Presentations}

\cvitem{March 3, 2026}{\emph{Latvian ditransitives: Evidence for a low applicative structure.} ECO-5 Workshop, Harvard University.\textsubscript{\href{https://sites.google.com/view/eco-5}{[abstract]}}}

\cvitem{Aug 2023}{\emph{Reframing Political Activism in East Germany.} College Summer Institute Closing Symposium, The University of Chicago.\textsubscript{\href{https://ccrf.uchicago.edu/2023-college-summer-institute-closing-symposium-proceedings\#Session5}{[abstract]}}}

\section{Manuscripts}

\cvitem{2026}
    {\emph{Scrambling in Latvian Double-Object Constructions.}
    \newline Unpublished manuscript.}

\cvitem{2025}
    {\emph{Insights from long-distance agreement in Blackfoot.}
    \newline Unpublished manuscript.}

\cvitem{2024}
    {\emph{Brazilian Portuguese \& The African Influence: logophoricity and null subjects.}
    \newline Unpublished manuscript.}

\cvitem{2023}
    {\emph{Indefinite null subjects in Brazilian Portuguese.}
    \newline Unpublished manuscript.}

\section{Research Experience}

\cvitem{Jun -- Aug\\ 2024}
    {\textbf{Research Assistant, Acquisition of Phonology in Brazilian Portuguese}
    \newline \textit{Prof. Raquel Santana Santos -- Language Acquisition Lab, University of São Paulo} 
    \newline Processed, edited, and catalogued audio recordings of toddlers and children acquiring Brazilian Portuguese.}

\cvitem{Jun 2023 -- May\\ 2024}
    {\textbf{Research Assistant, ``Subtitling the Fall of the Berlin Wall''}
    \newline \textit{Prof. Nicole G. Burgoyne -- Department of Germanic Studies, The University of Chicago}
    \newline Translated, captioned, and subtitled a set of interviews from German to English;
    \newline conducted and presented research on the language of activism.}

\cvitem{Jan -- Mar\\ 2023}
    {\textbf{Research Assistant, Annotation of Conversations in Aleut}
    \newline \textit{Madeline Snigaroff -- Department of Linguistics, The University of Chicago}
    \newline 	Annotated and categorized video recordings of language revitalization sessions; assisted in the creation of a database with speaker and recording metadata.}

\section{Service and Leadership}

\cvitem{To appear}
    {\textbf{Correa, Gabriel} and Kevin Morand (eds.). \emph{NELS 56: Proceedings of the fifty-sixth annual meeting of the North East Linguistics Society.} Amherst, MA: GLSA.}

\section{Other Service}

\cventry{Sep 2022 -- Aug\\ 2025}
    {Doc Films, The University of Chicago}{Chicago, IL}
    {Projectionist, Series Programmer\hfill {} \linebreak Winter 2024 Series: \emph{Class and Race in Brazilian Cinema}\textsubscript{\href{https://docfilms.org/archive/2024-series/winter/tuesday}{[link]}}}
    {}
    {}

\cventry{Feb -- May\\ 2024}
    {Library Student Advisory Council, The University of Chicago}{Chicago, IL}
    {Student Representative, Class of 2025}
    {}
    {}

\cventry{Feb 2021 -- Jun\\ 2022}
    {Wanderlust Initiative}{Remote (Brazil)}
    {Project Manager, Volunteer Language Tutor (English and German)}{}{}

\section{Languages}

\cvlistitem{Brazilian Portuguese (native)}
\cvlistitem{English (fluent)}
\cvlistitem{German (working knowledge)}
\cvlistitem{Spanish (reading knowledge)}
\cvlistitem{Korean (beginner)}

\section{Skills}

\cvitem{Proficient}{\LaTeX, Python, PCIbex Farm}
\cvitem{Basic}{R, HTML, CSS, Praat, ELAN}

% previous version:
% \cvitem{Coding}{Python (Pandas, NumPy, Matplotlib), R}
% \cvitem{Software}{\LaTeX, Praat, ELAN, Audacity, Aegisub}

\vspace{2em}
\cvlistitem{\slshape [Updated: June 2026]}

\end{document}